Read Me

### 2015-09-04 README.Rmd
another update to README

### analysis/
* ``ipm/`` -- contains R code for all analyses and figure production. 
    + ``sumlations/`` -- 
    + ``vitalRateRegs/`` -- 
* ``alpha_list_growth.csv`` -- CSV file with the alpha values used to define the spatial influence of genets on one another for the growth regressions (see [Chu and Adler 2015](http://www.esajournals.org/doi/abs/10.1890/14-1741.1))
* ``alpha_list_survival.csv`` -- CSV file with the alpha values used to define the spatial influence of genets on one another for the survival regressions (see [Chu and Adler 2015](http://www.esajournals.org/doi/abs/10.1890/14-1741.1))
* ``get_chainiter_sequence.R`` -- R script to make a random sequence chain and iteration draws so that all simulations use the same sequence of parameter values.
* ``get_year_sequence.R`` -- R script to make a random sequence year draws so that all simulations use the same sequence of climate years.

>>>>

### analysis/
* ``ipm/`` -- contains R code for all analyses and figure production. 
    + ``sumlations/`` -- 
        - ``another`` --
    + ``vitalRateRegs/`` -- 
* ``alpha_list_growth.csv`` -- CSV file with the alpha values used to define the spatial influence of genets on one another for the growth regressions (see [Chu and Adler 2015](http://www.esajournals.org/doi/abs/10.1890/14-1741.1))
* ``alpha_list_survival.csv`` -- CSV file with the alpha values used to define the spatial influence of genets on one another for the survival regressions (see [Chu and Adler 2015](http://www.esajournals.org/doi/abs/10.1890/14-1741.1))
* ``get_chainiter_sequence.R`` -- R script to make a random sequence chain and iteration draws so that all simulations use the same sequence of parameter values.
* ``get_year_sequence.R`` -- R script to make a random sequence year draws so that all simulations use the same sequence of climate years.
